---
title: Statistical analyses and plotting for experiments related to the effects of secondary metabolites produced by *Xylaria necrophora* on soybean leaves
author: "Teddy Garcia-Aroca"
date: "October 29, 2021"
output:
  pdf_document: default
  html_document: default
---

# Install packages needed.

## First, create a vector of all the packages needed:

```{r}
packages <- c("agricolae", "dplyr", "plyr", "ggplot2", "readr", "ggpubr", "car",
              "rcompanion", "tidyverse", "ggsignif", "reshape")
```

## Install packages not yet installed

```{r}
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}
```

## Load all packages
```{r}
invisible(lapply(packages, library, character.only = TRUE))
```

# Set the working directory to the directory where the output files will be saved.

In this example, we assume you have cloned/donwloaded this repository to your "Documents" folder.

Change directory on mac/linux:

setwd("/Users/YOURUSERNAME/Documents/X.necrophora.secondaryMetabolites/output")

Change directory on Windows (Windows 10 in this example):

setwd("C:/Users/YOURUSERNAME/Documents/X.necrophora.secondaryMetabolites/output")

## For this demosntration, we did not export the files in PDF to the output directory. If you wish to do so, do the following:

### Step 1: Call the pdf command to start the plot

    pdf(file = "/Users/YOURUSERNAME/Documents/X.necrophora.secondaryMetabolites/output/
    
    Figure1.pdf",   # The directory you want to save the file in

    width = 7, # The width of the plot in inches
    
    height = 5) # The height of the plot in inches
    
### Step 2: Add the code provided below for your desired plot.

### Step 3: Run dev.off() to create the file!

    dev.off()


## For this example, we set the working directory to the following:

```{r}
setwd("/Users/tedggarcia/Documents/X.necrophora.secondaryMetabolites/output/")
```

# Loading digital chlorophyll content datasets (only one repetition of each experiment for illustration purposes). All datasets can be found in the folder named "raw_data"

ES2 = First experiment for 14 Days of exporuse (DOE)

#ES4 = Repetetion for 14 DOE

ES5 = First experiment for 7 DOE

#ES8 = Repetition for 7 DOE

#ES13A = Experiment testing potentially resistant cultivars (7DOE)

ES13B = Repetition of ES13A

ES14A = Experiment testing effects among plant species (7DOE)

#ES14B = Repetition of ES14A

```{r}
ES2 <- read.csv("../raw_data/ES2.ChlorophyllContent.14DOE.Exp1.csv", header = T)
ES5 <- read.csv("../raw_data/ES5.ChlorophyllContent.7DOE.Exp1.csv", header = T)
ES13B <- read.csv("../raw_data/ES13B.ChlorophyllContent.7DOE.Exp2.Cultivars.csv",
                  header = T)
ES14A <- read.csv("../raw_data/ES14A.ChlorophyllContent.7DOE.Exp1.PlantSpecies.csv", 
                  header = T)
```

## Run Shapiro-Wilk Tests to check for normality

```{r}
shapiro.test(ES2$chl)
shapiro.test(ES5$chl)
shapiro.test(ES13B$chl)
shapiro.test(ES14A$chl)
```

## Check the distribution of the data and assess if normalization is needed.

```{r}
ggdensity(ES2$chl, main = "Density of Chlorophyll Content (digital) for ES2",
          xlab = "Datapoints")
ggdensity(ES5$chl, main = "Density of Chlorophyll Content (digital) for ES5", 
          xlab = "Datapoints")

ggdensity(ES13B$chl, main = "Density of Chlorophyll Content (digital) for ES13B", 
          xlab = "Datapoints")

ggdensity(ES14A$chl, main = "Density of Chlorophyll Content (digital) for ES14A", 
          xlab = "Datapoints")

ggqqplot(ES2$chl)
ggqqplot(ES5$chl)
ggqqplot(ES13B$chl)
ggqqplot(ES14A$chl)

plotNormalHistogram(ES2$chl, main = "Density of Chlorophyll Content (Digital) for ES2", 
                    xlab = "Datapoints")
plotNormalHistogram(ES5$chl, main = "Density of Chlorophyll Content (Digital) for ES5", 
                    xlab = "Datapoints")
plotNormalHistogram(ES13B$chl, main = "Density of Chlorophyll Content (Digital) for E13B",
                    xlab = "Datapoints")
plotNormalHistogram(ES14A$chl, main = "Density of Chlorophyll Content (Digital) for E14A",
                    xlab = "Datapoints")

```

## Use the Tukey's tranformation method to normalize the distribution and append to datasets

```{r}
ES2_chl.tuk = transformTukey(ES2$chl, plotit=FALSE)
ES5_chl.tuk = transformTukey(ES5$chl, plotit=FALSE)
ES13B_chl.tuk = transformTukey(ES13B$chl, plotit=FALSE)
ES14A_chl.tuk = transformTukey(ES14A$chl, plotit=FALSE)
```

## Append the transformed values to original datasets

```{r}
ES2.mod <- cbind(ES2, ES2_chl.tuk)
ES5.mod <- cbind(ES5, ES5_chl.tuk)
ES13B.mod <- cbind(ES13B, ES13B_chl.tuk)
ES14A.mod <- cbind(ES14A, ES14A_chl.tuk)
```

# Statistical analyses 

Run ANOVA and Tukey's honest significance differences for raw chlorophyll content.

## ES2 dataset (untransformed data)

As desribed above, this experiment was ran using cell-free culture filtrates (CFCFs) from three local strains of *Xylaria necrophora* (DMCC2126, DMCC2127, and DMCC2165) and one *Colletotrichum siamense* (DMCC2966) for 14 days (ES2)

```{r}
###############ES2 analysis (raw data)################################
ES2.chl.lm <- lm (ES2$chl ~ ES2$Treatment + 
                       ES2$Dilution + 
                       ES2$Condition + 
                       ES2$isoRep + 
                       ES2$techRep + 
                       ES2$sampleNumber)
ES2.chl.lm
summary(ES2.chl.lm)
anova(ES2.chl.lm)

#Tukey's HSD for Variable chl by Treament
ES2.chl.treatment.HSD.test <- HSD.test(ES2.chl.lm, 'ES2$Treatment', group = T)
ES2.chl.treatment.HSD.test

#Tukey's HSD for Variable chl by Dilution
ES2.chl.dilution.HSD.test <- HSD.test(ES2.chl.lm, 'ES2$Dilution', group = T)
ES2.chl.dilution.HSD.test


#Complete ANOVA for ES2 by treatment by dilution
ES2.comp.HSD.group <- HSD.test(ES2.chl.lm, c("ES2$Treatment", "ES2$Dilution"), group=TRUE,console=TRUE)

ES2.comp.HSD.group

```

## Same analysis using the normalized dataset

```{r}
###############ES2 analysis (normalized dataset) ################################
ES2.mod.chl.lm <- lm (ES2.mod$ES2_chl.tuk ~ ES2.mod$Treatment + 
                           ES2.mod$Dilution + 
                           ES2.mod$Condition + 
                           ES2.mod$isoRep + 
                           ES2.mod$techRep + 
                           ES2.mod$sampleNumber)
ES2.mod.chl.lm
summary(ES2.mod.chl.lm)
anova(ES2.mod.chl.lm)

#Tukey's HSD for Variable chl (tukey trans) by Treament
ES2.mod.chl.treatment.HSD.test <- HSD.test(ES2.mod.chl.lm, 'ES2.mod$Treatment', group = T)
ES2.mod.chl.treatment.HSD.test

#Tukey's HSD for Variable chl (tukey trans) by Dilution
ES2.mod.chl.dilution.HSD.test <- HSD.test(ES2.mod.chl.lm, 'ES2.mod$Dilution', group = T)
ES2.mod.chl.dilution.HSD.test


#Complete ANOVA for ES2.mod by treatment by dilution (tukey trans)
ES2.mod.comp.HSD.group <- HSD.test(ES2.mod.chl.lm, c("ES2.mod$Treatment", 
                                                        "ES2.mod$Dilution"), 
                                                        group=TRUE,console=TRUE)

ES2.mod.comp.HSD.group
```

## Run analyses for ES5

This test was run for 7 DOE and photos were taken of the last day of exposure.

```{r}
###############ES5 analysis################################
ES5.chl.lm <- lm (ES5$chl ~ ES5$Treatment + 
                               ES5$Dilution + 
                               ES5$Condition + 
                               ES5$isoRep + 
                               ES5$techRep + 
                               ES5$sampleNumber)
ES5.chl.lm
summary(ES5.chl.lm)
anova(ES5.chl.lm)

#Tukey's HSD for Variable chl by Treament
ES5.chl.treatment.HSD.test <- HSD.test(ES5.chl.lm, 'ES5$Treatment', group = T)
ES5.chl.treatment.HSD.test

#Tukey's HSD for Variable chl by Dilution
ES5.chl.dilution.HSD.test <- HSD.test(ES5.chl.lm, 'ES5$Dilution', group = T)
ES5.chl.dilution.HSD.test

#Tukey's HSD for Variable chl by Condition
ES5.chl.cond.HSD.test <- HSD.test(ES5.chl.lm, 'ES5$Condition', group = T)
ES5.chl.cond.HSD.test

#Complete ANOVA for ES5 by treatment by condition, by dilution
ES5.comp.HSD.group <- HSD.test(ES5.chl.lm, c("ES5$Treatment", "ES5$Condition", 
                                                "ES5$Dilution"), group=TRUE,console=TRUE)

ES5.comp.HSD.group
```

### Same analyses for ES5, using normalized data

```{r}
###############ES5 analysis (normalized data) ################################
ES5.mod.chl.lm <- lm (ES5.mod$ES5_chl.tuk ~ ES5.mod$Treatment +
                                                ES5.mod$Dilution + 
                                                ES5.mod$Condition + 
                                                ES5.mod$isoRep + 
                                                ES5.mod$techRep + 
                                                ES5.mod$sampleNumber)
ES5.mod.chl.lm
summary(ES5.mod.chl.lm)
anova(ES5.mod.chl.lm)

#Tukey's HSD for Variable chl (tukey trans) by Treament
ES5.mod.chl.treatment.HSD.test <- HSD.test(ES5.mod.chl.lm, 'ES5.mod$Treatment', 
                                           group = T)
ES5.mod.chl.treatment.HSD.test

#Tukey's HSD for Variable chl (tukey trans) by Dilution
ES5.mod.chl.dilution.HSD.test <- HSD.test(ES5.mod.chl.lm, 'ES5.mod$Dilution', 
                                          group = T)
ES5.mod.chl.dilution.HSD.test


#Tukey's HSD for Variable chl (tukey trans) by Condition
ES5.mod.chl.cond.HSD.test <- HSD.test(ES5.mod.chl.lm, 'ES5.mod$Condition', group = T)
ES5.mod.chl.cond.HSD.test

#Complete ANOVA for ES5.mod by treatment by condition, by dilution (tukey trans)
ES5.mod.comp.HSD.group <- HSD.test(ES5.mod.chl.lm, c("ES5.mod$Treatment",
                                                        "ES5.mod$Condition",
                                                        "ES5.mod$Dilution"),
                                                        group=TRUE,console=TRUE)
ES5.mod.comp.HSD.group
```

## Run analyses for ES13B

Testing variation among potentially resistant cultivars compared to known susceptible cultivars treated with CFCFs from *X. necrophora* (isolate DMCC 2165) to determine if resistance to direct application of SMs exist.

```{r}
#Statistical analysis
#####ES13B###
ES13B.chl.lm <- lm (ES13B$chl ~ ES13B$Treatment + 
                         ES13B$HostVariety + 
                         ES13B$isoRepNumber + 
                         ES13B$techRepNumber + 
                         ES13B$SampleNumber)
ES13B.chl.lm
summary(ES13B.chl.lm)
anova(ES13B.chl.lm)

#Tukey's HSD for Variable chl by Treatment
ES13B.chl.treatment.HSD.test <- HSD.test(ES13B.chl.lm, 'ES13B$Treatment', group = T)
ES13B.chl.treatment.HSD.test

#Tukey's HSD for Variable chl by Soybean Cultivar
ES13B.chl.host_variety.HSD.test <- HSD.test(ES13B.chl.lm, 'ES13B$HostVariety', group = T)
ES13B.chl.host_variety.HSD.test

#Complete ANOVA for ES13B
ES13B.comp.HSD.group <- HSD.test(ES13B.chl.lm, c("ES13B$Treatment", "ES13B$HostVariety"),
                                 group=TRUE,console=TRUE)

ES13B.comp.HSD.group

```

### Same analysis as above using the tukey normalized dataset

```{r}
#Statistical analysis
#####ES13B.mod###
ES13B.mod.chl.lm <- lm (ES13B.mod$ES13B_chl.tuk ~ ES13B.mod$Treatment + 
                             ES13B.mod$HostVariety + 
                             ES13B.mod$isoRepNumber + 
                             ES13B.mod$techRepNumber + 
                             ES13B.mod$SampleNumber)
ES13B.mod.chl.lm
summary(ES13B.mod.chl.lm)
anova(ES13B.mod.chl.lm)

#Tukey's HSD for Variable chl by Treatment
ES13B.mod.chl.treatment.HSD.test <- HSD.test(ES13B.mod.chl.lm, 'ES13B.mod$Treatment',
                                             group = T)
ES13B.mod.chl.treatment.HSD.test

#Tukey's HSD for Variable chl by Soybean Cultivar
ES13B.mod.chl.host_variety.HSD.test <- HSD.test(ES13B.mod.chl.lm,
                                                'ES13B.mod$HostVariety', group = T)
ES13B.mod.chl.host_variety.HSD.test

#Complete ANOVA for ES13B.mod
ES13B.mod.comp.HSD.group <- HSD.test(ES13B.mod.chl.lm, c("ES13B.mod$Treatment", 
                                                            "ES13B.mod$HostVariety"), 
                                                            group=TRUE,console=TRUE)

ES13B.mod.comp.HSD.group

```

## Run analyses for ES14A

This dataset contains chlorophyll content measured among plant species treated with CFCFs from *X. necrophora* (isolate DMCC 2165) to estimate the specificy of SMs.

```{r}
#####ES14A###
ES14A.chl.lm <- lm (ES14A$chl ~ ES14A$Treatment + 
                         ES14A$Host + ES14A$isoRepNumber + 
                         ES14A$techRepNumber + 
                         ES14A$LeafSampleNumber)
ES14A.chl.lm
summary(ES14A.chl.lm)
anova(ES14A.chl.lm)

#Tukey's HSD for Variable chl by Treatment
ES14A.chl.treatment.HSD.test <- HSD.test(ES14A.chl.lm, 'ES14A$Treatment', group = T)
ES14A.chl.treatment.HSD.test

#Tukey's HSD for Variable chl by Plant Species
ES14A.chl.host.HSD.test <- HSD.test(ES14A.chl.lm, 'ES14A$Host', group = T)
ES14A.chl.host.HSD.test

#Complete ANOVA for ES14A
ES14A.comp.HSD.group <- HSD.test(ES14A.chl.lm, c("ES14A$Treatment", "ES14A$Host"), group=TRUE,console=TRUE)

ES14A.comp.HSD.group
```

### Same analysis as above using Tukey's normalized data.

```{r}
#####ES14A.mod.mod###
ES14A.mod.chl.lm <- lm (ES14A.mod$ES14A_chl.tuk ~ ES14A.mod$Treatment + 
                             ES14A.mod$Host + 
                             ES14A.mod$isoRepNumber + 
                             ES14A.mod$techRepNumber + 
                             ES14A.mod$LeafSampleNumber)
ES14A.mod.chl.lm
summary(ES14A.mod.chl.lm)
anova(ES14A.mod.chl.lm)

#Tukey's HSD for Variable chl by Treatment
ES14A.mod.chl.treatment.HSD.test <- HSD.test(ES14A.mod.chl.lm, 'ES14A.mod$Treatment', group = T)
ES14A.mod.chl.treatment.HSD.test

#Tukey's HSD for Variable chl by Plant Species
ES14A.mod.chl.host.HSD.test <- HSD.test(ES14A.mod.chl.lm, 'ES14A.mod$Host', group = T)
ES14A.mod.chl.host.HSD.test

#Complete ANOVA for ES14A.mod
ES14A.mod.comp.HSD.group <- HSD.test(ES14A.mod.chl.lm, c("ES14A.mod$Treatment",
                                                            "ES14A.mod$Host"),
                                                            group=TRUE,console=TRUE)

ES14A.mod.comp.HSD.group
```

# Plotting individual plots and composite figures

## Individual plots for figure 1

Extract the information needed for panel "A"

```{r}
##Extract all control (ES5: 7 DOE)
ES5.control <- subset(ES5.mod, Treatment== "control")
ES5.Xn <- subset(ES5.mod, Treatment== c("DMCC2126", "DMCC2127", "DMCC2165"))

ES5.control <- ES5.control %>%
  add_column(Species = "control")

ES5.Xn <- ES5.Xn %>%
  add_column(Species = "X.necrophora")

ES5.mod.v2 <- rbind(ES5.control, ES5.Xn)


ES5.mod.ggplot <- ggplot(ES5.mod.v2, aes(x = reorder(Species, -chl, na.rm = TRUE), 
                                         y = chl, fill = Species)) + 
  geom_boxplot() + #geom_point(aes(colour = factor(LeafSampleNumber)))# + geom_jitter()
  #scale_fill_grey(start = 1, end = 0.4) + labs(tag = "A") +
  scale_fill_manual(values = c("#FFFFFF", "#545454"))+ labs(tag = "A") +
  xlab("Treatment") + ylab("Total Chlorophyll (ng/sq mm)") + 
  theme(plot.title = element_text(size = 12, hjust = 0.1, face = "bold"),
        axis.title.x = element_text(size=10, face = "bold"), 
        axis.title.y = element_text(size = 10, face = "bold"), 
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + 
  facet_wrap(~ Dilution)
ES5.mod.ggplot
```

## Individual plot for panel B

```{r}
##Extract all control (ES2), colletrichum, and X. necrophora
ES2.control <- subset(ES2.mod, Treatment== "control")
ES2.coll <- subset(ES2.mod, Treatment== "DMCC2966")
ES2.Xn <- subset(ES2.mod, Treatment== c("DMCC2126", "DMCC2127", "DMCC2165"))

ES2.control <- ES2.control %>%
  add_column(Species = "control")

ES2.coll <- ES2.coll %>%
  add_column(Species = "C.siamense")

ES2.Xn <- ES2.Xn %>%
  add_column(Species = "X.necrophora")

ES2.mod.v2 <- rbind(ES2.control, ES2.coll, ES2.Xn)

#plot for figure by species by dilution factor

#Reorganizing for plotting

ES2.mod.v2$Species <- factor(ES2.mod.v2$Species,                 
                         levels = c("control", "C.siamense", "X.necrophora"))

ES2.mod.v2.ggplot <- ggplot(ES2.mod.v2, aes(x = reorder(Species, -chl, na.rm = TRUE),
                                            y = chl, fill = Species)) + geom_boxplot() + #geom_point(aes(colour = factor(LeafSampleNumber)))# + geom_jitter()
 # scale_fill_grey("control" = 1, "C.siamense" =0.7, "X.necrophora"= 0.4) 
  scale_fill_manual(values = c("#FFFFFF", "#AAAAAA", "#545454"))+ labs(tag = "B") +
  xlab("Treatment") + ylab("Total Chlorophyll (ng/sq mm)") + 
  theme(plot.title = element_text(size = 12, hjust = 0.1, face = "bold"), 
        axis.title.x = element_text(size=10, face = "bold"), 
        axis.title.y = element_text(size = 10, face = "bold"), 
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black")) + 
  facet_wrap(~ Dilution)
ES2.mod.v2.ggplot
```

## Plot composite figure 1


```{r}

###Grid for composite figure 1 (updated 10/25/2021). Using ES2 and ES5 only.
gridExtra::grid.arrange(ES5.mod.ggplot, ES2.mod.v2.ggplot, ncol=2)
```

## Plotting individual plots and composite figure 3

### Individual panels A, B, C, and D.


```{r}
###Plot HostVariety only w/ outliers
ES13B.ByHosCult <- ggplot(ES13B.mod, aes(x = reorder(HostVariety, -chl, na.rm = TRUE), 
                                         y = chl, fill=HostVariety)) + 
  geom_boxplot() +
  scale_fill_grey(start = 1, end = 0.4) + labs(tag = "A") + 
  xlab("Soybean Cultivar") + ylab("Total Chlorophyll (ng/sq mm)") + 
  theme(plot.title = element_text(size = 12, hjust = 0.1, face = "bold"), 
        axis.title.x = element_text(size=10, face = "bold"), 
        axis.title.y = element_text(size = 10, face = "bold"), 
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black")) 
ES13B.ByHosCult
```

# Individual panel B

```{r}
###Plot by variety by treatment w/ outliers
ES13B.ggplot.ByCultByTreat <- ggplot(ES13B.mod, aes(x = reorder(HostVariety, -chl, 
                                                                na.rm = TRUE), 
                                                    y = chl, fill=Treatment)) +
  geom_boxplot() + #+ geom_point(aes(colour = factor(LeafSampleNumber)))# + geom_jitter()
    scale_fill_grey(start = 1, end = 0.4) + labs(tag = "B") + 
    xlab("Soybean Cultivar") + ylab("Total Chlorophyll (ng/sq mm)") + 
    theme(plot.title = element_text(size = 12, hjust = 0.1, face = "bold"), 
          axis.title.x = element_text(size=10, face = "bold"), 
          axis.title.y =element_text(size = 10, face = "bold"), 
          axis.text.x = element_text(angle = 45, hjust = 1)) + 
    theme(panel.border = element_blank(), 
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          axis.line = element_line(colour = "black")) 
ES13B.ggplot.ByCultByTreat
```

## Panel C

```{r}
###Plot By Host only w/ outliers for grid
ES14A.ggplot.ByHost <- ggplot(ES14A.mod, aes(x = reorder(Host, -chl, na.rm = TRUE), 
                                             y = chl, fill=Host)) + 
  geom_boxplot() + #+ geom_point(aes(colour = factor(LeafSampleNumber)))# + geom_jitter()
    scale_fill_grey(start = 1, end = 0.4) + labs(tag = "C") + 
    xlab("Plant Species") + ylab("Total Chlorophyll (ng/sq mm)") + 
    theme(plot.title = element_text(size = 12, hjust = 0.1, face = "bold"), 
          axis.title.x = element_text(size=10, face = "bold"), 
          axis.title.y = element_text(size = 10, face = "bold"), 
          axis.text.x = element_text(angle = 45, hjust = 1)) + 
    theme(panel.border = element_blank(), 
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          axis.line = element_line(colour = "black")) 
ES14A.ggplot.ByHost 
```

## Panel D

```{r}
###Plot by host by treatment w/ outliers
ES14A.ggplot.ByHostByTreat <- ggplot(ES14A.mod, aes(x = reorder(Host, -chl, na.rm = TRUE),
                                                    y = chl, fill=Treatment)) +
  geom_boxplot() + #+ geom_point(aes(colour = factor(LeafSampleNumber)))# + geom_jitter()
  scale_fill_grey(start = 1, end = 0.4) + labs(tag = "D") +
    xlab("Plant Species") + ylab("Total Chlorophyll (ng/sq mm)") + 
    theme(plot.title = element_text(size = 12, hjust = 0.1, face = "bold"), 
          axis.title.x = element_text(size=10, face = "bold"), 
          axis.title.y = element_text(size = 10, face = "bold"), 
          axis.text.x = element_text(angle = 45, hjust = 1)) + 
    theme(panel.border = element_blank(), 
          panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
          axis.line = element_line(colour = "black")) 
ES14A.ggplot.ByHostByTreat 
```

## Composite figure 3

```{r}
###Grid for composite figure 3 (08/16/2021). Using ES13B and ES14 only.
gridExtra::grid.arrange(ES13B.ByHosCult,
                        ES13B.ggplot.ByCultByTreat , 
                        ES14A.ggplot.ByHost, 
                        ES14A.ggplot.ByHostByTreat, ncol=2)
```

# Supplementary Materials/Figures

## Plotting Supplementary Figure 1

```{r}

#ES2 by treatment by dilution, by growth conditions no title
ES2.mod.ggplot.v2 <- ggplot(ES2.mod, aes(x = reorder(Treatment, -chl, na.rm = TRUE), 
                                         y = chl, fill = Dilution)) + 
  geom_boxplot() + #geom_point(aes(colour = factor(LeafSampleNumber)))# + geom_jitter()
  scale_fill_grey(start = 1, end = 0.4) + labs(tag = "A") +
  xlab("Treatment") + ylab("Total Chlorophyll (ng/sq mm)") + 
  theme(plot.title = element_text(size = 12, hjust = 0.1, face = "bold"), 
        axis.title.x = element_text(size=10, face = "bold"),
        axis.title.y = element_text(size = 10, face = "bold"), 
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black")) 
ES2.mod.ggplot.v2


#ES5 by treatment by dilution, no title
ES5.mod.ggplot.v2 <- ggplot(ES5.mod, aes(x = reorder(Treatment, -chl, na.rm = TRUE), 
                                         y = chl, fill = Dilution)) + 
  geom_boxplot() + #geom_point(aes(colour = factor(LeafSampleNumber)))# + geom_jitter()
  scale_fill_grey(start = 1, end = 0.4) + labs(tag = "B") +
  xlab("Treatment") + ylab("Total Chlorophyll (ng/sq mm)") + 
  theme(plot.title = element_text(size = 12, hjust = 0.1, face = "bold"),
        axis.title.x = element_text(size=10, face = "bold"), 
        axis.title.y = element_text(size = 10, face = "bold"), 
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black")) + 
  facet_wrap(~ Condition)
ES5.mod.ggplot.v2

#ES5 by conditions (side by side)
ES5.mod.ggplot.v3 <- ggplot(ES5.mod, aes(x = reorder(Condition, -chl, na.rm = TRUE), 
                                         y = chl, fill=Treatment)) + 
  geom_boxplot() +
  scale_fill_grey(start =1, end = 0.4) + labs(tag = "C") +
  xlab("Growth Condition") + ylab("Total Chlorophyll (ng/sq mm)") + 
  theme(plot.title = element_text(size = 12, hjust = 0.1, face = "bold"), 
        axis.title.x = element_text(size=10, face = "bold"), 
        axis.title.y = element_text(size = 10, face = "bold"), 
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black")) 
ES5.mod.ggplot.v3 

#ES5 by dilutions (side by side)
ES5.mod.ggplot.v4 <- ggplot(ES5.mod, aes(x = reorder(Dilution, -chl, na.rm = TRUE), 
                                         y = chl, fill=Treatment)) + 
  geom_boxplot() +
  scale_fill_grey(start =1, end = 0.4) + labs(tag = "D") +
  xlab("Dilution Factor") + ylab("Total Chlorophyll (ng/sq mm)") + 
  theme(plot.title = element_text(size = 12, hjust = 0.1, face = "bold"), 
        axis.title.x = element_text(size=10, face = "bold"), 
        axis.title.y = element_text(size = 10, face = "bold"), 
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black")) 
ES5.mod.ggplot.v4


###Grid for supplementary figure 1 (updated 08/25/2021). Using ES2 and ES5 only.
gridExtra::grid.arrange(ES2.mod.ggplot.v2, 
                        ES5.mod.ggplot.v2, 
                        ES5.mod.ggplot.v3,ES5.mod.ggplot.v4, ncol=2)

```

# Plotting Supplementary Figure 2

This composite figure contained validation chlorophyll content (chemical vs digital extractions) on panel A, fungal biomass based on Whatmat No 1 filter weight on panel B, measurements of pH from initial potato dextrose broth and filtered stock cell-free culture filtrates (CFCFs) on panel C, and the pearson correlation between final pH and digital chlorophyll content on panel D.


## Loading datasets for composite figure

```{r}
#Load datasets
ES10.chem <- read.csv("../raw_data/ES10.chem.chl.csv", header = T)
#Chlorophyll content obtained chemically for a dataset with all biomass and pH measurements

ES10.digital <- read.csv("../raw_data/ES10.digital.chl.csv", header = T)
#Chlorophyll content obtained digitally for a dataset with all biomass and pH measurements

BiomassAndpH.metadata <- read.csv("../raw_data/FilteringTreatments.metadata.csv", 
                                  header = T)
```

### Summarizing and aggregating datasets

```{r}
#Obtaining sums for ES10  because digital measurements=3 per experimental unit,
#but chemical measurements=1 per experimental unit. 

ES10.digital.sum <- aggregate(ES10.digital$chl,list(ES10.digital$ExpCode),sum)

names(ES10.digital.sum)[names(ES10.digital.sum) == "x"] <- "dig.chl"

#Merging ES10 chem and ES10 digital
ES10.chem.dig = merge(ES10.chem, ES10.digital.sum, by.x='ExpCode', by.y='Group.1')
```



```{r}
#Pearson correlations for ES10
cor(ES10.chem.dig$chl, ES10.chem.dig$dig.chl, method="pearson")
```

## Plotting Supplementary Figure 2 panel A

```{r}
ES10.chem.dig.ggplot <- ggscatter(ES10.chem.dig, x = "chl", y = "dig.chl", 
                                                          add = "reg.line", conf.int = TRUE,
                                                          cor.coef = TRUE, 
                                                          cor.method = "pearson",
                                  xlab = "Chemical chlorophyll content (ng/sq mm)", 
                                  ylab = "Digital chlorophyll content (ng/sq mm)") + 
                                                          labs(tag = "A")
ES10.chem.dig.ggplot
```

## Plotting Biomass by Treatment by Condition 

(Supplementary Figure 2, Panel B)

```{r}
# Supplementary figure 2 panel B
## ES5 by dilutions (side by side)
BiomassAndpH.metadata.ggplot.B <- ggplot(BiomassAndpH.metadata, 
                                         aes(x = reorder(Isolate, +Weight_grams), 
                                             y = Weight_grams, fill=FilterWeight)) +
  geom_boxplot() + #geom_point(aes(colour = factor(LeafSampleNumber)))# + geom_jitter()
  scale_fill_grey(start =0.4, end = 1) + labs(tag = "B") +
  xlab("Treatment") + ylab("Whatman No. 1 Filter Weight (grams)") + 
  theme(plot.title = element_text(size = 12, hjust = 0.1, face = "bold"), 
        axis.title.x = element_text(size=10, face = "bold"), 
        axis.title.y = element_text(size = 10, face = "bold"), 
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black")) +
  facet_wrap(~ Condition)
BiomassAndpH.metadata.ggplot.B
```

## Supplementary figure 2 panel C

```{r}
#ES5 by dilutions (side by side)
BiomassAndpH.metadata.pH.ggplot.C <- ggplot(BiomassAndpH.metadata, 
                                            aes(x = reorder(Isolate, +pH), 
                                                y = pH, fill=pHMeasurement)) +
  geom_boxplot() + 
  scale_fill_grey(start =0.4, end = 1) + labs(tag = "C") +
  xlab("Treatment") + ylab("pH") + 
  theme(plot.title = element_text(size = 12, hjust = 0.1, face = "bold"), 
        axis.title.x = element_text(size=10, face = "bold"), 
        axis.title.y = element_text(size = 10, face = "bold"), 
        axis.text.x = element_text(angle = 45, hjust = 1)) + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black")) +
  facet_wrap(~ Condition)
BiomassAndpH.metadata.pH.ggplot.C
```


## Supplementary figure 2 panel D

```{r}
ES8.chem <- read.csv("../raw_data/ES8_chem.chl.csv", header = T)
ES8.digital <- read.csv("../raw_data/ES8.digital.chl.csv", header = T)


ES8.digital.sum <-aggregate(ES8.digital$chl,list(ES8.digital$ExpCode),sum)
names(ES8.digital.sum)[names(ES8.digital.sum) == "x"] <- "dig.chl"

ES8.chem.dig = merge(ES8.chem, ES8.digital.sum, by.x='ExpCode', by.y='Group.1')


FinalpHvsChl.reg <- ggscatter(ES8.chem.dig, x = "dig.chl", y = "FinalpH", 
                                          add = "reg.line", conf.int = TRUE, 
                                          cor.coef = TRUE, cor.method = "pearson",
                                          xlab = "Digital chlorophyll content (ng/sq mm)",
                                          ylab = "Final pH") + labs(tag = "D")
FinalpHvsChl.reg
```

## Supplementary Figure 2 composite. Updated on 08/02/2021 

```{r}
gridExtra::grid.arrange(ES10.chem.dig.ggplot, BiomassAndpH.metadata.ggplot.B, BiomassAndpH.metadata.pH.ggplot.C, FinalpHvsChl.reg, ncol=2)
```

# Plotting Supplementary Figure 3


# Loading dataset (root growth)

```{r}
ES2.root <- read.csv("../raw_data/ES2.rootMeasurements.csv", header = T)

#Clean dataset for plotting and analyses
ES2.root.noNAs <- na.omit(ES2.root)
```

## Statistical analyses for root lenght

```{r}
#ES2 longest root statistical analysis
ES2.root.noNAs.lm <- lm (ES2.root.noNAs$Length ~ ES2.root.noNAs$Isolate + ES2.root.noNAs$Condition + ES2.root.noNAs$Concentration, na.action=na.exclude)
ES2.root.noNAs.lm
summary(ES2.root.noNAs.lm)
anova(ES2.root.noNAs.lm)

#Tukey's HSD for Variable Condition

ES2.root.noNAs.condition.HSD.test <- HSD.test(ES2.root.noNAs.lm, 
                                              'ES2.root.noNAs$Condition', group = T)
ES2.root.noNAs.condition.HSD.test

#Tukey's HSD for Variable Concentration

ES2.root.noNAs.Concentration.HSD.test <- HSD.test(ES2.root.noNAs.lm, 'ES2.root.noNAs$Concentration', group = T)
ES2.root.noNAs.Concentration.HSD.test

#Tukey's HSD for Variable Isolate

ES2.root.noNAs.isolate.HSD.test <- HSD.test(ES2.root.noNAs.lm, 'ES2.root.noNAs$Isolate', group = T)
ES2.root.noNAs.isolate.HSD.test

#Tukey's HSD for Treatment and concentration
ES2.root.noNAs.leafsec.treat.dil.HSD.test <- HSD.test(ES2.root.noNAs.lm, c('ES2.root.noNAs$Isolate', 'ES2.root.noNAs$Concentration'), group = T )
ES2.root.noNAs.leafsec.treat.dil.HSD.test
```

## Comparison after normalization of data

```{r}
# Used the same Tukey's normalization methods used above
ES2.root.tuk = transformTukey(ES2.root.noNAs$Length, plotit=FALSE)

ES2.root.noNAs.mod = cbind(ES2.root.noNAs, ES2.root.tuk)

#ES2 longest root statistical analysis after normalization
ES2.root.noNAs.mod.lm <- lm (ES2.root.noNAs.mod$ES2.root.tuk ~ ES2.root.noNAs.mod$Isolate + 
                               ES2.root.noNAs.mod$Condition +
                               ES2.root.noNAs.mod$Concentration, na.action=na.exclude)
ES2.root.noNAs.mod.lm
summary(ES2.root.noNAs.mod.lm)
anova(ES2.root.noNAs.mod.lm)

#Tukey's HSD for Variable Condition

ES2.root.noNAs.mod.condition.HSD.test <- HSD.test(ES2.root.noNAs.mod.lm, 'ES2.root.noNAs.mod$Condition', group = T)
ES2.root.noNAs.mod.condition.HSD.test

#Tukey's HSD for Variable Concentration

ES2.root.noNAs.mod.Concentration.HSD.test <- HSD.test(ES2.root.noNAs.mod.lm, 'ES2.root.noNAs.mod$Concentration', group = T)
ES2.root.noNAs.mod.Concentration.HSD.test

#Tukey's HSD for Variable Isolate

ES2.root.noNAs.mod.isolate.HSD.test <- HSD.test(ES2.root.noNAs.mod.lm, 'ES2.root.noNAs.mod$Isolate', group = T)
ES2.root.noNAs.mod.isolate.HSD.test

#Tukey's HSD for Treatment and concentration
ES2.root.noNAs.mod.leafsec.treat.dil.HSD.test <- HSD.test(ES2.root.noNAs.mod.lm, c('ES2.root.noNAs.mod$Isolate', 'ES2.root.noNAs.mod$Concentration'), group = T )
ES2.root.noNAs.mod.leafsec.treat.dil.HSD.test

```

# Plotting Supplementary Figure 3

```{r}
#Plate for Supp Figure 3 FINAL (USE THIS ONE, because no differences between Shaking and stat were observed)
ES2.root.noNAs.mod$Isolate  <- with(ES2.root.noNAs.mod, reorder(Isolate, -Length))
ES2.root.noNAs.mod.ggplot.plate <- ggplot(ES2.root.noNAs.mod, aes(x = Isolate, 
                                                                  y = Length, 
                                                                  fill = Isolate)) + 
  geom_boxplot() +
  #scale_fill_grey(start = 1, end = 0.4) +
  #scale_fill_manual(values = c("Control"="green", "DMCC2966"="green", "DMCC2126"="gold", "DMCC2165"="gold", "DMCC2127"="gold"))+ 
  #ggtitle("Root Length at 14 Days After Exposure") +
  scale_fill_manual(values = c("#000000", "#FFFFFF", "#DADADA", "#ACACAC","#666666")) +
  xlab("Treatment") + ylab("Root Length (mm)") + 
  theme(plot.title = element_text(size = 14, hjust = 0.5, face = "bold"), 
        axis.title.x = element_text(size=10, face = "bold"), 
        axis.title.y = element_text(size = 10, face = "bold"), 
        axis.text.x = element_text(angle = 30, hjust = 1)) +
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black")) +
  facet_wrap(~ Concentration)
ES2.root.noNAs.mod.ggplot.plate
#dev.off()
```


